### 2024-07-01 Scripts/Manuscript/manuscript.Rmd
Incorporated feedback on the entire text from co-authors. Removed two figures, checked grammar.

---
title             : "An Empirical Assessment of Reliable and Valid Measurement as a Prerequisite for Informative Replications"
shorttitle        : "Measurement Quality and Informative Replications"

author: 
  - name          : "Goos, C."
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Professor Cobbenhagenlaan 125, 5037 DB, Tilburg, The Netherlands"
    email         : "casgoos99@gmail.com"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Data curation"
      - "Formal Analysis"
      - "Investigation"
      - "Methodology"
      - "Project Administration"
      - "Software"
      - "Visualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Bakker, M."
    affiliation   : "1"
    role:
      - "Supervision"
      - "Writing - Review & Editing"
  - name          : "Wicherts, J.M."
    affiliation   : "1"
    role:
      - "Supervision"
      - "Writing - Review & Editing"
  - name          : "Nuijten, M.B."
    affiliation   : "1"
    role:
      - "Conceptualization"
      - "Project Administration"
      - "Supervision"
      - "Validation"
      - "Writing - Review & Editing"

@@

abstract: |
  Psychological science has been facing threats to the credibility of its findings, particularly due to the lack of replicability of findings.
  Recently, there has been increasing attention towards the impact that features of psychological measurement, specifically reliability and measurement reporting, has on replicability.
  In this article, we assessed the reliability and measurement reporting within the Many Labs replications and the original studies they were based on. 
  We then empirically investigated the associations of replicability with reliability and measurement reporting.
  The results indicated that not all measures were sufficiently reliable across contexts. 
  Additionally, reliability and validity evidence was rarely reported. 
  Finally, incompleteness in measurement reporting was associated with lower replicability of the findings tested with that measure.
  The results not only indicate potential issues in reliability and validity of measures, but also that incomplete measurement reporting may negatively affect replicability. 
  These findings illustrate the importance of reliable measurement, and complete measurement reporting for establishing credible findings. 
  The article ends with suggestions to improve measurement reporting. 
  We further suggest that the reported measurement information should be evaluated when  researchers decide what studies to replicate.

keywords          : "reliability, validity, measurement, measurement reporting, replicability, credibilitys"
wordcount         : "182"

@@

@@

# manually retrieving the Rstudio version
rstudioapi::versionInfo()
```

@@

# Introduction

For solid scientific progress in psychology, we need to be able to rely on previous findings - findings should be credible. Unfortunately, psychology seems to face several threats to the credibility of its findings. In this article, we investigate how the credibility of psychological findings may be affected by problems in psychological measurement, and in turn, how those problems may affect successful replication.

### Credibility & Replicability

A prerequisite for a credible finding is that it is replicable [@vazire2022CredibilityReplicabilityImproving]. This means that the observed effect should be comparable across the original study and subsequent replications as long as the differences between them are believed to be of little relevance to the effect [@nosek2022replicability].

In practice, effects deviate substantially between original and replication research. In 2015, the Replication Project: Psychology (RPP) attempted replications of 100 research findings in psychology, they observed a substantial discrepancy between the replication findings as compared to the original findings [@osc2015estimating]. Similarly, the Many Labs projects replicated the effects reported in original articles across different labs in various locations around the world [@klein2014investigating; @camerer2016evaluating; @camerer2018evaluating; @ebersole2016many; @ebersole2020many; @klein2018many; @klein2022many]. There it was observed that effects were on average smaller in replication compared to original research. Furthermore, there was variation within the estimates of the effect between different lab locations.

In response to this string of failed replications, there was widespread alarm regarding the credibility and robustness of findings in psychological science [@hughes2018psychology; @giner2019crisis]. Simultaneously researchers sought to explain this discrepancy. The factors that have been proposed include, questionable research practices [@simmons2011false; @john2012measuring; @cumming2014new; @wicherts2016degrees], questionable reporting practices [@bakker2011mis; @nuijten2016prevalence], and biased publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science]. A factor that has gained more traction recently is the impact of measurement-related challenges on replicability.

### Credibility & Measurement

Measurement in psychological science is characterized in large part by one overarching issue: psychological constructs, such as affective state or intelligence, can usually not be measured directly [@flake2017construct]. As a result, psychologists face two primary challenges in the use of measurement: First of all, because the measurement is indirect, it also comes with some degree of random error surrounding its assessment. Secondly, the responses on the measure have to relate to the psychological construct(s) of interest, but as the construct is not directly observable, this is difficult to assess.

The first issue relates to the concept of reliability, which gives an indication of how consistent the responses on a measurement are. Reliability is a critical first step to obtaining credible findings. Because if the scores on a measure are not consistent with themselves, it is unlikely that any effect associated with the measure can be consistently established.

The second issue relates to the concept of validity, and specifically construct validity. Validity in measurement refers to the overall extent to which a measure measures what it is supposed to [@borsboom2004concept], while construct validity refers to the substantial relation between the scores on a measure and the related psychological construct. A researcher cannot assume to have found a credible psychological effect, if the measures do not relate to a psychological construct [@cook2002experimental].

### Replicability & Measurement

Whereas both reliable and valid measurement and replicability are important elements that independently contribute to the overall credibility of a finding, there may also be a relation between the two. Indeed, recent studies have illustrated that both the reliability of the measure [@stanley2014expectations] and the reporting of the measure [@shaw2020measurement; @flake2017construct; @flake2020measurement] can affect the credibility of psychological studies, and in turn explain the lack of replication success. This study aims to investigate the influence of both measurement reliability and measurement reporting on replicability, using data and reports from the large scale Many Labs replication projects.

### Many Labs Sample Description

In the Many Labs projects each effect was directly replicated across multiple lab locations over the world. As a result the data obtained from these measures allows us to say something about the variability in these measures across different contexts. Another important aspect of the Many Labs projects is that the measurement was preregistered and documented in structured protocols that were used to instruct all the participating labs. We believe that these represent some of the best practices in measurement usage in psychology. Therefore, any problems with the measurement and its reporting encountered in this sample would not bode well for measurement in the rest of psychology.

@@

While reliability is generally considered a measure specific feature, this is false. The reliability of a measure is context dependent [@cho2015cronbach; @pauly2018resampling], and as a result so are the scores obtained with that measure. The contextual variations in the measurement scores could explain the discrepancy between effects in original and replication research, as well as within replications of the same original effect. Besides random variation due the sampling error, the variations can also reflect true variation in reliability, also known as reliability heterogeneity [@vacha-haase1998ReliabilityGeneralizationExploring]. For instance, measures are known to generally show lower reliability in more homogeneous samples as compared to heterogeneous samples [@pike1998reliability].

However, even when reliability is the same across studies, reliability can still cause estimates of the same effect to vary significantly. @stanley2014expectations simulated data of items on a scale based on levels of sampling error and reliability similar to what is standard in psychological research. The results indicated that measurement error due to imperfect reliability caused variation in the observed effect sizes in the simulated replications, on top of sampling error. The added variation was substantial enough to cause replications of a positive small effect to observe anywhere between a medium negative effect and a large positive effect [@stanley2014expectations]. This implies that studies using unreliable measures have a lower probability to be successfully replicated, even if the underlying effect is true and the measurement is equally reliable between original and replication.

@@

Despite the importance of having reliable and valid measures, research has shown that Questionable Measurement Practices (QMPs) in reporting are not uncommon. QMPs are practices that raise doubts about a measurement's validity [@flake2020measurement], and have been coined as a conjugate term to Questionable Research Practices [QRPs, @john2012measuring]. QMPs range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of measure and procedure of any sourced measures [@flake2020measurement].

@flake2020measurement identified the main questions that the article should answer in relation to the measurement used: the definition of the construct, how the measure was selected, how the measure was operationalized, how the measure was quantified, whether it was modified or not and why, and the reasons and details of creating a measure if applicable. The questions together form the basis of the information that a researcher should present in order to be transparent and promote a more cumulative psychological science.

@flake2022construct documented QMPs among 100 replications and their respective original articles from the RPP [@osc2015estimating]. They coded the number of measures, the number of items in the measure, and the information that was reported describing the measure and providing evidence justifying its use. Besides limited reporting of validity and reliability evidence for the coded measures, @flake2022construct found that several of the measures in the RPP did not report the number of items, the response format, or the scoring of the scale. Furthermore, only 8 of the 40 translated scales contained validity evidence for the translated version of the scale. Measures were similarly modified between original and replication in other ways without evidence showing that the modification did not invalidate the measurement.

Further findings by @flake2022construct and others [@flake2017construct; @shaw2020measurement] illustrated how QMPs create challenges for replicating researchers. Replicating researchers will need detailed information on the measurement in the original study to reconstruct it. If the measure is not reconstructed exactly, original and replication may be measuring different construct(s). In that case, different effect size estimates in original compared to replication research may very well be due to the fact that the effects are between different constructs, and not because the effect was not robust to sampling error.

@@

Our study aimed to investigate the influence of both measurement reliability and measurement reporting on replicability, using data and reports from the large scale Many Labs replication projects. Firstly, this study expands on the research by @stanley2014expectations using an empirical example. Our goal was to see whether reliability was related to replication success on real life replication data. In practical terms, we investigated whether or not replicated studies differed in their reliability scores from non-replicated studies. In their study @stanley2014expectations assumed reliability to be constant across studies, which we know to be an oversimplification. Therefore, to add further context to relation between reliability and replication, this study also investigated the variation in reliability as observed across separate measurement occasions.

@@

## Research Questions & Hypotheses:

@@

Measurement reliability varies across contexts. It is crucial for evaluating replications that differences between replication and original are understood and accounted for.

-   RQ1a. What is the degree of score reliability in replications of psychological research?
-   RQ1b. What is the degree of score reliability in original psychological research?

@@

-   H1. No difference is present in the degree of score reliability between replication research and original psychological research.

Reliability has the potential to vary not only between replication and original research, but also within replications of the same effect [@vacha-haase1998ReliabilityGeneralizationExploring].

-   RQ2. To what degree do reliability estimates differ within a replication set of the same original study?

Heterogeneity could be a major contributor to this variation. However for effect sizes there is little empirical evidence of widespread heterogeneity among the Many Labs replications [@klein2018many; @olsson2020heterogeneity]. The same is expected to hold true for the heterogeneity in reliability coefficients among the Many Labs replications.

@@

In order to see if reliability has an impact on replication attempts, we investigated whether or not successfully replicated studies differ in the reliability of their measures as compared to non-replicated studies.

-   RQ3. What is the association between replication study score reliability and replication outcome?

Greater reliability means the variance around the estimate of the true effect is decreased [@nunnally1994assessment]. Assuming that the true effect is not null, then the statistical conclusions tested with reliable measures are be more likely to converge to significance.

-   H3. Score reliability in replication research is positively associated with successful replication of an original finding.

@@

With respect to measurement reporting, this study first of all aims to conceptually replicate some of the findings of @flake2022construct.

-   RQ4a. To what degree are QMPs present in replications of psychological research?
-   RQ4b. To what degree are QMPs present in original psychological research?

@flake2022construct found that QMPs were overall more common in the RPP replications as compared to the original research. We did not hypothesize this same effect to hold for the Many Labs sample, because of the use of structured protocols documenting the measurement.

-   H4. QMPs are expected to be more frequent in original psychological research than in replication research.

Differences in measurement resulting from QMPs have been suspected to cause replication and original effects to deviate [@flake2022construct]. Investigating the link between QMPs and non-replicability should put this suspicion to the test.

@@

A reduction in QMPs corresponds to greater transparency in reporting of measurement. Research on other transparency related practices have shown that these are associated with more robust estimates of effects [@wicherts2011willingness; @protzko2020high]. We expect a similar effect for QMPs.

-   H5. QMPs in replication research are negatively associated with successful replication of an original finding.

One of the reasons measurement in replication may deviate is because original articles did not report all the necessary information needed to mimic the original measurement. In this way a lack of information may carry over from the original article to the replication.

@@

Previous research by @flake2022construct has shown that QMPs in original articles cause issues for recreating measurements for replication research. Additionally, @shaw2020measurement found similar spill-over effects for validity. Based on these findings, QMPs in original research were expected to be associated with QMPs in replication research.

-   H6. Total number of QMPs in original psychological research is positively related to total number of QMPs in replication research.

@@

Data collection, coding protocol, and planned analyses were all preregistered. The preregistration and supplementary materials can be found on this article's OSF page: <https://osf.io/9r8yt/>. Any deviations from the preregistration are explicitly mentioned in the text.

@@

This manuscript was created in Rstudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency. All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> & <https://osf.io/9r8yt/>.

@@

We report how we determined all data exclusions, all manipulations, and all measures in the study. Our sample size was based on the number of usable studies in the Many Labs studies.

@@

This research was approved by the Tilburg University School of Social and Behavioral Sciences Ethical Review Board.

@@

The data used for the analyses in this study consists of three main sources: replication datasets, preregistered replication protocols, and original study articles. The data came from the Many Labs series of studies. In particular, data from Many Labs 1, 2, 3, & 5 was used [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many]. Data from Many Labs 4 [@klein2022many] was not part of the sample, as there was no publicly available protocol which contains the information needed to code QMPs. Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study's focus on item-based measures.

@@

Measures were identified using the preregistered replication protocols. Acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses were not included. The result was a total sample size of `r nrow(coded_data_replications)` measures used in both original and replication research[^1].

[^1]: Initially the original articles contained 3 more measures than the replication protocols. This difference was due to the way that the moral foundations questionnaire was framed in the original articles compared to in the original article. In the original article it was framed as measuring five different moral foundations, while in the replication protocol the measure was described as measuring the two overarching categories that were used to test the main effect in the original and replication research. The measurement information reported was comparable across all five categories, and thus it was deemed that the measurement could be reduced to reflect two overarching categories to make comparison between original and replication easier.

@@

The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. Both the replication protocols and replication datasets were scanned through to ensure that the planned analyses were feasible. However, no coding or analysis of either of them had taken place before the analyses were preregistered. Further details on the search strategy can be found in the [coding protocol information file](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) supplementary materials.

@@

The replication datasets refer to the publicly available datasets containing the data obtained from all of the labs that took part in one of the Many Labs studies. These datasets were accessed through their OSF page. For the analyses, the scores on the items of an identified measure were identified and extracted. When scores could not be clearly identified, any available codebooks, analysis scripts or study materials were used to identify the relevant scores.

In order to be considered suitable for the planned analyses on calculated reliabilities, the measure had to be a scale consisting of multiple items. If cleaned data was available this was chosen over raw data, to ensure that variables were coded as intended (e.g. no reverse-coded items). Pilot data were omitted from the analyses entirely. These criteria resulted in suitable item score data from `r apa_num(length(unique(data_h3_multiple$g)), numerals = FALSE)` replication sets spread across on average `r apa_num(mean(table(data_h3_multiple$g)), digits = 0)` lab locations for the analyses of hypotheses 2 & 3.

@@

### Preregistered Replication Protocols

The preregistered replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each set of replications replicating a single original study across multiple labs.

The OSF page for each Many Labs project was combed through, in order to identify the documents that contained information on the measurement practice and reported reliability. For Many Labs 2, & 3 a single replication protocol for all studies could be identified. For Many Labs 1, the Proposal_V1.1 provided the equivalent information, while for Many Labs 5 protocols were available for each set of replications separately.

The relevant OSF page of each replication set was searched through for a file which contained protocol in its name. If available, a version of the protocol labelled as revised, post-review, peer-review, or endorsed was selected. Otherwise, the latest uploaded relevant protocol was selected. Protocols labelled as data collection, analysis protocol or anything similar were excluded[^2].

[^2]: The steps taken to access the replication protocol data from Many Labs 5 were not preregistered, and only became clear upon further investigation of the accessible information. The specific names and locations of the files that were used as the datasets can be found in the data_search_details.pdf supplementary materials of this article <https://osf.io/gft46/%7D>.

Finally, the published reports of the Many Labs projects [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many] were used to determine whether not the replication was considered successful.

@@

The original study articles are the published articles of the original effect on which the Many Labs replication sets were based. They were identified using the citations for these articles in each replication protocol. In the end all articles could be retrieved through searches on Web of Science, Google Scholar, and PsychInfo (in that order)[^3].

[^3]: An issue was encountered while trying to access @hyman1950current. However, after contacting the first author of @klein2014investigating a suitable version of the article was obtained.

@@

A structured coding protocol (available on the relevant OSF: <https://osf.io/9r8yt/>, and github pages: <https://github.com/CasGoos/measurement_and_replication.git>) was used to extract information on the reported measurement evidence and reporting quality for both replication protocols and original studies. The coding protocol and explanation of its use can be found in the coding protocols folder of the supplementary materials.

@@

Because data from the Many Labs replications was available for each lab location within a replication set, it was possible to calculate score reliabilities for the item scale measure used for each lab location separately. This made it possible to assess the variation of score reliabilities of the same measure across different contexts.

Cronbach's alpha was calculated as the main score reliability index used in the analyses, as it remains the most commonly used indicator of the reliability of a measure [@flake2017construct]. This is important for facilitating comparison between the calculated replication reliabilities and the reported original article reliabilities. Cronbach's alpha was calculated using the alpha function from the psych R package [@R-psych]. Default arguments were used for the function. Omega was pre-registered as an additional reliability index score, because it is regarded by numerous psychometricians as a more informative alternative to Cronbach’s Alpha. The results based on Omega can be found in [Appendix C](AppendixScripts/Appendix_multilevel_analyses.Rmd).

@@

In order to answer questions regarding reported reliability, the reported reliability coefficient of a measure was extracted from both the replication protocols and the original articles when present. Both the type (Cronbach's alpha, retest, interrater, etc.) and the value itself were extracted. Similarly, we coded the presence of any validity evidence, such as a factor analysis, alongside the measure. The aim here was to gauge the presence of factor analyses within the articles and protocols, for comparison with @shaw2020measurement.

>>>>

---
title             : "An Empirical Assessment of Reliable and Valid Measurement as a Prerequisite for Informative Replications"
shorttitle        : "Measurement and Informative Replications"

author: 
  - name          : "Goos, C."
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Professor Cobbenhagenlaan 125, 5037 DB, Tilburg, The Netherlands"
    email         : "c.goos@tilburguniversity.edu"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Data curation"
      - "Formal Analysis"
      - "Investigation"
      - "Methodology"
      - "Project Administration"
      - "Software"
      - "Visualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Bakker, M."
    affiliation   : "1"
    role:
      - "Supervision"
      - "Writing - Review & Editing"
  - name          : "Wicherts, J.M."
    affiliation   : "1"
    role:
      - "Supervision"
      - "Writing - Review & Editing"
  - name          : "Nuijten, M.B."
    affiliation   : "1"
    role:
      - "Conceptualization"
      - "Project Administration"
      - "Supervision"
      - "Validation"
      - "Writing - Review & Editing"

@@

abstract: |
  The credibility of psychological science and the ability to replicate earlier findings require good measurement.
   Here, we assessed the reliability and measurement reporting of 77 measures within 56 Many Labs replications and related original psychological studies. 
   We investigated their associations with replicability.
   The results indicated that not all measures in the original and replication studies were sufficiently reliable across contexts. 
   Additionally, evidence on reliability and validity was rarely reported. 
   Finally, incompleteness in measurement reporting in replication studies was associated with lower replicability of the findings tested with that measure. 
   These findings indicate a worrying lack of reported validating evidence for measurement in the literature, and its harm to credibility.
   We offer suggestions on improving measurement validation and reporting practices, and argue that researchers should evaluate the reported measurement information when deciding what studies to replicate.

keywords          : "reliability, validity, measurement, reporting, replicability, credibility"
wordcount         : "135"

@@

header-includes:
  - |
    \makeatletter
    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-1em}%
      {\normalfont\normalsize\bfseries\typesectitle}}

    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-\z@\relax}%
      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
    \makeatother

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"

@@

# manually retrieving the Rstudio version
rstudioapi::versionInfo()

@@

<!-- Introduction -->

For solid scientific progress in psychology, we need to be able to rely on previous findings - findings should be credible. Unfortunately, psychology seems to face several threats to the credibility of its findings. In this article, we investigate how the credibility of psychological findings may be affected by problems in psychological measurement, and in turn, how those problems may affect subsequent replications.

## Credibility & Replicability

A prerequisite for a credible finding is that it is replicable [@vazire2022CredibilityReplicabilityImproving]. This means that the observed effect should be comparable across the original study and subsequent replications if the differences between them are believed to be of little relevance to the effect [@nosek2022replicability].

But replications often fail. In 2015, the Replication Project: Psychology (RPP) attempted replications of 100 research findings in psychology, they observed a substantial discrepancy between the replication findings and the original findings [@osc2015estimating]. Similarly, the Many Labs projects aimed to replicate the effects reported in original articles across different labs in various locations around the world [@klein2014investigating; @ebersole2016many; @ebersole2020many; @klein2018many; @klein2022many], and often found smaller effects in replications compared to original research. Furthermore, the estimates of the effect varied between different lab locations.

In response to this string of failed replications, there was widespread alarm regarding the credibility and robustness of findings in psychological science [@hughes2018psychology; @giner2019crisis], and efforts to explain failures to replicate. The factors that have been proposed include, questionable research practices [@simmons2011false; @john2012measuring; @cumming2014new; @wicherts2016degrees], questionable reporting practices [@bakker2011mis; @nuijten2016prevalence], and biased publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science]. Another factor that has gained more traction recently is the impact of measurement-related challenges on replicability and credibility.

## Credibility & Measurement

Psychological constructs, such as affective state or intelligence, can not be measured directly [@flake2017construct]. Psychological measurements involve random measurement errors and uncertainties about whether the targeted construct is indeed well reflected in the scores retrieved from the measurement procedure.

The first issue relates to the concept of reliability, which gives an indication of how consistent the responses on a measurement are. Reliability is a critical first step to obtaining credible findings. Because if the scores on a measure are not consistent with themselves, it is unlikely that any effect associated with the measure can credibly be established. Psychometrics offers various ways to assess reliability empirically [e.g. @nunnally1978overview; @mellenbergh2011conceptual].

The second issue relates to the concept of validity, specifically construct validity, or the overall extent to which a measure measures what it is supposed to  measure [@borsboom2004concept]. Construct validity of test scores is often assessed by comparing the test scores’ empirical associations to the theoretical associations of the constructs [@cronbach1955construct]. A researcher cannot claim to have found a credible psychological effect, if the measures do not relate to the psychological construct [@cook2002experimental].

## Replicability & Measurement

While reliable and valid measurement, as well as replicability are important elements that independently contribute to the overall credibility of a finding, there may also be a relation between them. Indeed, recent studies have illustrated that both the reliability of the measure [@stanley2014expectations] and the reporting of information relevant to demonstrating the validity of the measurement [@shaw2020measurement; @flake2017construct; @flake2020measurement] may be related to the chance of successfully replicating a psychological finding. This study aims to investigate the relation of reliability and measurement reporting with replicability, using data and reports from the large scale Many Labs replication projects.

## Many Labs Sample Description

Because the Many Labs projects involved multiple lab locations over the world directly replicating the same effect, their data allows us to study the variability in these measures across different contexts. Furthermore, the Many Labs projects used preregistered and documented structured protocols, we therefore believe the measurement use in these projects represent a high standard within the field. Any issues in measurement here is thus taken as an indication that other replications are equally if not more likely to face the same issues.

@@

While reliability is generally considered a measure specific feature, this is false. The reliability of a measure varies between samples, and thus  [@cho2015cronbach; @pauly2018resampling]. Besides random variation due the sampling error, the variations can also reflect true variation in reliability, also known as reliability heterogeneity [@vacha-haase1998ReliabilityGeneralizationExploring]. For instance, measures are known to generally show lower reliability in more homogeneous samples as compared to heterogeneous samples [@pike1998reliability].

The resulting variations in the measurement scores could contribute to the discrepancy between effects in original and replication research, as well as within replications of the same original effect. After all it has long been known that noise in measurement suppresses observed effects and associations [@spearman1904proof]. @stanley2014expectations simulated data of items on a scale based on levels of sampling error and reliability similar to what is standard in psychological research. The results showed that the variation due to measurement error was substantial enough to cause replications of a positive small effect to observe anywhere between a medium negative effect and a large positive effect [@stanley2014expectations]. In summary, studies using unreliable measures are less replicable, even when the measurement is equally reliable between original and replication.

@@

Despite the importance of having reliable and valid measures, research has shown that Questionable Measurement Practices (QMPs) are not uncommon. QMPs are practices that raise doubts about a measurement's validity [@flake2020measurement], and have been coined as a conjugate term to Questionable Research Practices [QRPs, @john2012measuring]. QMPs range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of measure and procedure of any sourced measures [@flake2020measurement]. More specifically,  @flake2020measurement identified six key questions than an article should answer to avoid QMPs: the definition of the construct, how the measure was selected, how the measure was operationalized, how the measure was quantified, whether it was modified or not and why, and the reasons and details of creating a measure if applicable. If these questions can be answered based on the reported measurement information, then reporting is sufficiently transparent to promote a more cumulative psychological science.

@flake2022construct documented QMPs among 100 replications and their respective original articles from the RPP [@osc2015estimating]. They coded the number of measures, the number of items in the measure, and the information that was reported describing the measure and providing evidence justifying its use. Besides limited reporting of validity and reliability evidence for the coded measures, @flake2022construct found that several of the measures in the RPP did not report the number of items, the response format, or the scoring of the scale. Furthermore, only eight of the 40 translated scales contained validity evidence for the translated version of the scale. Measures were similarly modified between original and replication in other ways without evidence showing that the modification did not invalidate the measurement.

Further findings by @flake2022construct and others [@flake2017construct; @shaw2020measurement] also illustrated how QMPs create challenges for replicating researchers. In order to reconstruct the measurement, replication researchers need to know the items that were used, how they were presented to the subjects, and how to compute the scores. If the measure is not reconstructed exactly, constructs measured by original and replication may differ. leading to differences in effect size estimates irrespective of the credibility of the original effect.

@@

Our study investigated the relation of reliability and measurement reporting with replicability, using data and reports from the large scale Many Labs replication projects. First, this study expands on the research by @stanley2014expectations. Our goal was to see whether reliability was related to replication success on empirical replication data. Specifically, we investigated whether replicated studies differed in their reliability from non-replicated studies.  @stanley2014expectations assumed reliability to be constant across studies, which we know to be an oversimplification. Therefore, to add further context to the relation between reliability and replication, this study also investigated the variation in reliability as observed across labs.

@@

## Research Questions & Hypotheses

@@

Measurement reliability varies across samples. It is crucial for evaluating replications that differences between replication and original are understood and accounted for.

-   RQ1a. What is the reliability in replications of psychological research?
-   RQ1b. What is the reliability in original psychological research?

@@

-   H1. No difference is present in the reliability between replication research and original psychological research.

Reliability has the potential to vary not only between replication and original research, but also across replicating labs assessing the same effect [@vacha-haase1998ReliabilityGeneralizationExploring].

-   RQ2. Do reliability estimates differ between replicating labs?

Heterogeneity in reliability may be contributing strongly to the variation in reliability between labs. However, for effect sizes there is little empirical evidence of widespread heterogeneity among the Many Labs replications [@klein2018many; @olsson2020heterogeneity]. We expect the same for the heterogeneity in reliability coefficients.

@@

To see if reliability is related to replication success, we investigated whether successfully replicated studies differ in the reliability of their measures as compared to non-replicated studies.

-   RQ3. What is the association between replication study reliability and replication outcome?

Greater reliability means the variance around the estimate of the true effect is decreased [@nunnally1994assessment]. Assuming that the true effect is not null, then the statistical conclusions tested with reliable measures are more likely to converge to significance.

-   H3. Reliability in replication research is positively associated with successful replication of an original finding.

@@

This study aims to conceptually replicate the findings on measurement reporting of @flake2022construct.

-   RQ4a. How common are QMPs in replications of psychological research?
-   RQ4b. How common are QMPs in original psychological research?

@flake2022construct found that QMPs were overall more common in the RPP replications as compared to the original research. We did not hypothesize this to be the case in the Many Labs sample, because of the use of structured protocols documenting the measurement.

-   H4. QMPs are more frequent in original psychological research than in replication research.

QMPs obscure information relevant to mimic measurement from original research in subsequent replication attempts. The resulting deviations in measurement may be partly responsible for deviations in replication and original effects [@flake2022construct].

@@

A reduction in QMPs corresponds to greater transparency in reporting of measurement. In line with earlier research finding other transparency related practices to be associated with more robust estimates of effects [@wicherts2011willingness; @protzko2020high], we expect:

-   H5. QMPs in replications are negatively associated with replication success.

QMPs obscure information about a particular measurement. This in turn may cause issues for reconstructing that measurement in subsequent replication attempts.

@@

@flake2022construct already proposed that QMPs in original articles may cause issues for recreating measurements for replication research. @shaw2020measurement already found such a spill-over effect for validity. In line with this research we expect:

-   H6. The total number of QMPs in original psychological research is positively related to the total number of QMPs in replication research.

@@

We preregistered data collection, coding protocol, and planned analyses: <https://osf.io/9r8yt/>. Deviations from the preregistration are explicitly mentioned in the text.

@@

This manuscript was created in RStudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency. All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> and <https://osf.io/9r8yt/>.

@@

We report how we determined all data exclusions, all manipulations, and all measures in the study. Our sample size was predetermined by the number of studies in the Many Labs projects.

@@

This research was approved by the Tilburg University School of Social and Behavioral Sciences Ethical Review Board (nr. TSB_TP_REMA06).

@@

The data used for the analyses consisted of three main sources: replication datasets, replication protocols, and original study articles. The data came from the Many Labs replication projects. Specifically, data from Many Labs 1, 2, 3, & 5 [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many]. Many Labs 4 [@klein2022many] was excluded, as there was no publicly available replication protocol. Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study's focus on item-based measures.

@@

The unit of analysis in this study was a measure of a psychological construct used in the primary analysis that was being replicated.  We used the the replication protocols to identify these measures. Acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses were not included.

@@

We retrieved the data on the replication protocols, and replication datasets of Many Labs 1, 2, 3, & 5 from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. Both the replication protocols and replication datasets were scanned through to ensure that the planned analyses were feasible. However, no coding or analysis of either of them had taken place before the analyses were preregistered. Further details on the search strategy can be found in the [coding protocol information file](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) in the supplementary materials.

@@

The replication datasets refer to the publicly available datasets containing the data obtained from all labs that took part in a Many Labs study. For the analyses, we extracted the scores on the items of each previously identified measure that met our inclusion criteria specified below. When scores could not be clearly identified, any available codebooks, analysis scripts or study materials were used to identify the relevant scores.

To be included in the planned analyses on calculated reliabilities, the measure had to be a scale consisting of multiple items. If cleaned data was available this was chosen over raw data, to ensure that variables were coded as intended (e.g. no reverse-coded items). Pilot data were omitted from the analyses entirely. These criteria resulted in suitable item score data from `r apa_num(length(unique(data_h3_multiple$g)))` replication sets spread across on average approximately `r apa_num(mean(table(data_h3_multiple$g)), digits = 0)` lab locations for the analyses of Hypotheses 2 & 3.

@@

### Replication Protocols

The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each set of replications replicating a single original study across multiple labs. These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [Data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document.

@@

The original study articles were identified using the citations for these articles in each replication protocol. All articles could be retrieved.

@@

We developed and used a coding protocol (the [coding protocol](../../SupplementaryMaterials/CodingProtocols/Measurement_Error_Reporting_Revised_Coding_Protocol.pdf) is available in the supplementary materials) to extract information on the reported measurement evidence and reporting quality for both replication protocols and original studies.

@@

Because data from the Many Labs replications were available for each lab location within each replication set, it was possible to calculate reliabilities for any item scale measure used for each lab location separately. This made it possible to assess the variation of reliabilities of the same measure across different contexts.

Cronbach's Alpha was calculated as the main reliability index used in the analyses, as it remains the most commonly used indicator of the reliability of a measure [@flake2017construct], thus allowing for comparisons with the reliabilities reported in original articles. Cronbach's Alpha was calculated using the alpha function from the psych R package [@R-psych] with default arguments. Omega was pre-registered as an additional index of reliability, because it is regarded by numerous psychometricians as a more informative alternative to Cronbach’s Alpha [@crutzen2017scale; @deng2017testing]. The results based on Omega can be found in [Appendix C](AppendixScripts/Appendix_multilevel_analyses.Rmd).

@@

We extracted the reported reliability coefficient and type of index (Cronbach's Alpha, retest, interrater, etc.) of a measure from both the replication protocols and the original articles when present. Similarly, we coded the presence of any validity evidence, such as a factor analysis, that was presented alongside the measure.
